---
title: "Homework-01"
author: "DingHuan,3170102085"
output: pdf_document
---
1. a. Noticing that the data in iowa.csv is seperated by ";", I choose to add an argument `sep = ";"` to the funtion `read.csv()`.
    ```{r}
    iowa.df <- read.csv("data/iowa.csv", header = T, sep = ";")
    head(iowa.df)
    ```
    b. There are 33 rows and 10 columns.
    ```{r}
    dim(iowa.df)
    ```
    c. The names of the columns are shown below.
    ```{r}
    colnames(iowa.df)
    ```
    d. The value of row 5, column 7 of `iowa.df` is 79.7.
    ```{r}
    iowa.df[5,7]
    ```
    e. The second row of `iowa.df` is shown below.
    ```{r}
    iowa.df[2,]
    ``` 

2. a. The first line creates a vector of characters(or strings) named `vactor1`.
    ```{r}
    vector1 <- c("5", "12", "7", "32")
    ```
    The second line calculate the maximum of the strings in `vector1` according to the lexicographical order. Given that `"1" < :3" < "5" < "7"`, we get the answer of `max(vector1)` `"7"`.
    ```{r}
    max(vector1)
    ```
    The third line arranges strings in `vector1` from small to large. Reconsidering the analysis above, we get the answer below.
    ```{r}
    sort(vector1)
    ```
    The fourth line gets an error, because `sum()` can only calculate the numeric arguments, rather than strings.
    ```{r error=T}
    sum(vector1)
    ```
    b. The first series of commands produce an error, because the first line create an character variable named `vector2`, whose components are characters `"5","7","12"` as a result of the inability of a vector variable to save multiple types of data. However, the addition operation of characters `+` is not defined in R.
    ```{r, error = T}
    vector2 <- c("5",7,12)
    vector2[2] + vector2[3]
    ```
    The second series of commands returns 19, because a dataframe variable can save different types of data, so the addition of numeric data 7 and 12 is equal to `19`.
    ```{r, error = T}
    dataframe3 <- data.frame(z1="5",z2=7,z3=12)
    dataframe3[1,2] + dataframe3[1,3]
    ```
    The third series of commands also produce an error at the third line. The first line create a list variable, whose 2nd and 4th components are numerical. The second line add the 2th component to the 4th one as values, returning an answer 168. However, the syntax `list4[2]` returns `z2 = 42` as a list, thun an error occurs because the addition operation of lists `+` is not defined in R.
    ```{r, error = T}
    list4 <- list(z1="6", z2=42, z3="49", z4=126)
    list4[[2]]+list4[[4]]
    list4[2]+list4[4]
    ```
    
3. a. Use arguments `by` and `length.out` in `seq()` to achieve the target.
    ```{r}
    seq(1, 10000, by = 372)
    seq(1, 10000, length.out = 50)
    ```
    b. `rep(1:3, times = 3)` repeat the total vector `1:3` for 3 times, returning an vector `1 2 3 1 2 3 1 2 3`. `rep(1:3, each = 3)` repeat each components in vector `1:3` for 3 times separately, returning an vector `1 1 1 2 2 2 3 3 3`.
    ```{r}
    rep(1:3, times = 3)
    rep(1:3, each = 3)
    ```

4. (MB.CH1.2) 
    ```{r, message = F}
    library(DAAG)
    library(tidyverse)
    data(orings)
    pre.launch <- orings[c(1,2,4,11,13,18),]
    pre.launch %>% ggplot(aes(x = Temperature, y = Total)) +
      geom_point() +
      labs(title = "6 rows of the data set")
    ```
    ```{r}
    orings %>% ggplot(aes(x = Temperature, y = Total)) +
      geom_point() + 
      labs(title = "The full data set")
    ```
    
5. (MB.CH1.4) a. There's no column holds missing values.
    ```{r}
    data(ais)
    str(ais)
    which(!complete.cases(ais))
    ```
    b. There is a large imbalance in the numbers of the two sexes in gym, netball, T_sport and W_polo.
    ```{r}
    Sports <- levels(ais$sport)
    ST = matrix(nrow = 2, ncol = length(Sports), 
                dimnames = list(c('male', 'female'),Sports))
    for (i in 1:length(Sports)){
      ST[1,i] <- sum((ais$sex == 'm') & (ais$sport == Sports[i]))
      ST[2,i] <- sum((ais$sex == 'f') & (ais$sport == Sports[i]))
    }
    print(ST)
    ```
    ```{r}
    balance = ST['male',] / ST['female',]
    names(which(balance < 0.5 | balance > 2))
    ```
6. (MB.CH1.6) 
    ```{r}
    Manitoba.lakes <- data.frame(
      elevation = c(217,254,248,254,253,227,178,207,217),
      area = c(24387,5374,4624,2247,1353,1223,1151,755,657))
    row.names(Manitoba.lakes) <- c('Winnipeg','Winnipegosis','Manitoba','SouthernIndian',
                                   'Cedar','Island','Gods','Cross','Playgreen')
    ```
    a. 
    ```{r, warning = F}
    attach(Manitoba.lakes)
    plot(log2(area) ~ elevation, pch=16, xlim=c(170,280))
    text(log2(area) ~ elevation, labels=row.names(Manitoba.lakes), pos=4)
    text(log2(area) ~ elevation, labels=area, pos=2)
    title("Manitoba’s Largest Lakes")
    ```
    b. 
    ```{r, warning = F}
    plot(area ~ elevation, pch=16, xlim=c(170,280), ylog=T)
    text(area ~ elevation, labels=row.names(Manitoba.lakes), pos=4, ylog=T)   
    text(area ~ elevation, labels=area, pos=2, ylog=T)
    title("Manitoba’s Largest Lakes")
    ```
7. (MB.CH1.7) 
    ```{r, warning = F}
    dotchart(Manitoba.lakes$area, xlab = "area")
    text(Manitoba.lakes$area[-1],2:9,labels=row.names(Manitoba.lakes[-1,]), pos = 4)
    text(Manitoba.lakes$area[1],1,labels=row.names(Manitoba.lakes[1,]), pos = 2)
    title("Manitoba’s Largest Lakes")
    ```
    ```{r, warning = F}
    dotchart(Manitoba.lakes$area, xlab = "area (on a logarithmic scale)", log = "x")
    text(Manitoba.lakes$area[-1],2:9,labels=row.names(Manitoba.lakes[-1,]), pos = 4)
    text(Manitoba.lakes$area[1],1,labels=row.names(Manitoba.lakes[1,]), pos = 2)
    title("Manitoba’s Largest Lakes")
    ```