---
title: "Homework-01"
author: "DingHuan,3170102085"
output: pdf_document
---
1. The Iowa data set iowa.csv is a toy example that summarises the yield of wheat (bushels per acre) for the state of Iowa between 1930-1962. In addition to yield, year, rainfall and temperature were recorded as the main predictors of yield.
    a. First, we need to load the data set into R using the command `read.csv()`. Use the help function to learn what arguments this function takes. Once you have the necessary input, load the data set into R and make it a data frame called `iowa.df`.
    b. How many rows and columns does `iowa.df` have? 
    c. What are the names of the columns of `iowa.df`?
    d. What is the value of row 5, column 7 of `iowa.df`?
    e. Display the second row of `iowa.df` in its entirety.
    
    **Solve**. Noticing that the data in iowa.csv 
    a. 
    ```{r}
    iowa.df <- read.csv("data/iowa.csv", header = T, sep = ";")
    ```
    b. 
    ```{r}
    dim(iowa.df)
    ```
    c. 
    ```{r}
    colnames(iowa.df)
    ```
    d. 
    ```{r}
    iowa.df[5,7]
    ```
    e. 
    ```{r}
    iowa.df[2,]
    ``` 

2. Syntax and class-typing.
    a. For each of the following commands, either explain why they should be errors, or explain the non-erroneous result.
    ```
    vector1 <- c("5", "12", "7", "32")
    max(vector1)
    sort(vector1)
    sum(vector1)
    ```
    b. For the next series of commands, either explain their results, or why they should produce errors.
    ```
    vector2 <- c("5",7,12)
    vector2[2] + vector2[3]
    
    dataframe3 <- data.frame(z1="5",z2=7,z3=12)
    dataframe3[1,2] + dataframe3[1,3]
    
    list4 <- list(z1="6", z2=42, z3="49", z4=126)
    list4[[2]]+list4[[4]]
    list4[2]+list4[4]
    ```
    
    **Solve**. 
    a. 
    ```{r}
    vector1 <- c("5", "12", "7", "32")
    ```
    
    ```{r}
    max(vector1)
    ```
    ```{r}
    sort(vector1)
    ```

    b. 
    ```{r}
    vector2 <- c("5",7,12)
    vector2[2] + vector2[3]
    ```